### 2017-02-27 pkg/Pmisc/inst/docs/document.Rmd
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/diseasemapping@1658 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

knitr::opts_chunk$set(
  echo=FALSE, prompt=TRUE, comment=NA,
		margins=1, fig.cap=' ',
		fig.width=2.75, fig.height=2.75,  dpi=250, 
		tidy=TRUE, tidy.opts=list(indent=2, width.cutoff=55)
)

@@

```{r theHeader, echo=FALSE}
Pmisc::markdownHeader(
	title="Example of an html document with subfigures", 		
	author='Patrick Brown',
	slides=FALSE,
	bibliography = bibFile,
	geometry='margin=1in',
	csl = system.file('src','apa-no-doi-no-issue.csl', package='Pmisc'),
	css = system.file('src','article.css', package='Pmisc')
)
```

@@

for(D in knitr::opts_current$get()$fig.subcap) {
  hist(runif(100))
}
```

@@

mdTable(x=mytable, digits=3,
  caption = 'the table', caption.loc='bottom')

>>>>

knitr::opts_chunk$set(
  echo=FALSE, prompt=TRUE, comment=NA,
		margins=1, fig.cap=' ', fig.pos='ht',
		fig.width=2.75, fig.height=2,  dpi=250, 
		tidy=TRUE, tidy.opts=list(indent=2, width.cutoff=55)
)

@@

```{r theHeader, echo=FALSE}
Pmisc::markdownHeader(
	title="Example of a simple R markdown document with subfigures", 		
	author='Patrick Brown',
	bibliography = bibFile,
	geometry='margin=1in',
	csl = system.file('src','apa-no-doi-no-issue.csl', package='Pmisc'),
	css = system.file('src','article.css', package='Pmisc')
)
```

@@

for(D in knitr::opts_current$get()$fig.subcap) {
  hist(runif(100), main='')
}
```

@@

Pmisc::mdTable(x=mytable, digits=3,
  caption = 'the table', caption.loc='bottom', 
  where = 'htb')
